---
title: "Romer_Pfactor_20190626_CTSA"
author: "Maria Sison and Annchen Knodt"
date: "6/26/2019 - 12/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache = TRUE, fig.path = 'Figs/')
```

## Image Processing

1. HCP minimal structural preprocessing pipelines
  - includes subcortical volume aseg atlas (FreeSurfer)
2. Surface Glasser parcellation

## Analysis

### libraries and files
```{r libraries,results='hide'} 
library(pwr)
library(plyr)
library(readxl)
library(GGally)
library(caret)
library(forestplot)
library(foreign)
corrCT_19 <- read.csv("H:/Database/DBIS/Imaging/HCPMPP/corrCT_HCPMPP.csv", header = TRUE, na.strings=".")
SA_19 <- read.csv("H:/Database/DBIS/Imaging/HCPMPP/SA_HCPMPP.csv", header = TRUE, na.strings=".")
TOT_19 <- read.csv("H:/Database/DBIS/Imaging/HCPMPP/Structural_wholebrain_HCPMPP.csv", header = TRUE, na.strings=".")
aseg_19 <- read.csv("H:/Database/DBIS/Imaging/HCPMPP/aseg_HCPMPP.csv", na.strings=".")
workdir <- "H:/Projects/Annchen/DBIS/P/CTSA/"
```

### Measures of T1 quality, inc Euler characteristic
```{r euler}
aseg_summary <- read.csv("H:/Database/DBIS/Imaging/FreeSurfer/v6.0/FreeSurfer_aseg_SummaryMeasures.csv", na.strings=".")
T1_QC <- read.csv("H:/Database/DBIS/Imaging/QC/T1_QC.csv", na.strings=".", skip=2)
averageFD <- read.csv("H:/Database/DBIS/Imaging/QC/fMRI_QC_averageFD.csv")
averageFD$ID <- sub("sub-","DMHDS",averageFD$bidsid)
QC_merged <- merge(aseg_summary, merge(T1_QC, averageFD, by="ID"), by="ID")

png(paste(workdir, "T1QC_ManualRatingVsEuler.png", sep=""), height=4, width=6, res=150, units="in")
  plot(QC_merged$Visual.rating, QC_merged$SurfaceHoles, xlab="Manual QC rating", ylab="Euler characteristic (# surface holes)")
dev.off()

cor.test(QC_merged$Visual.rating, QC_merged$SurfaceHoles)
cor.test(QC_merged$Visual.rating, QC_merged$AverageFD)
QC_merged$snum <- as.numeric(as.character(sub("DMHDS", "", QC_merged$ID)))
```

### set up phase 45 P factor
```{r files}
# base file
DBISbase <- read.csv("H:/Collaborations/DBIS_ImagingBaseFile.csv", header = TRUE)
# P 45 update
LittleP <- read.csv("H:/Database/DBIS/P45_pFactor_June2019.csv", header = TRUE)
# match original variable names
names(LittleP) <- c("snum","EXT_B","INT_B","P_B","EXT_CF","INT_CF","THD_CF")
# reorder columns
LittleP <- subset(LittleP,select=c(1,4:7,2,3))
# add Gender
LittleP <- merge(DBISbase,LittleP,by="snum")
names(LittleP)[2] <- "sex"
LittleP$sex <- as.factor(LittleP$sex)
# adding covariates for response to reviews, 11/3/19
covars <- read.spss(paste(workdir,"Romer_addns.sav",sep=""),to.data.frame = TRUE,use.value.labels=FALSE)
names(covars)[1] <- "snum"
covars$AnyRxPsych45 <- as.factor(covars$AnyRxPsych45)
scanMeds <- read.csv(paste0(workdir, "ScanTimeMeds.csv"))
scanMeds$BrainMed_bin <- ifelse(scanMeds$BrainMed>0,1,0)
LittleP <- merge(LittleP,merge(covars,merge(QC_merged[,c("snum","SurfaceHoles","AverageFD","Visual.rating")], scanMeds, by="snum"),by="snum"),by="snum")
```

### inclusive list (14 subjects excluded)
```{r inclusive list}
# inclusive list: all 1 and 1f
LOG_master_inclusion_list <- read.csv("H:/Database/DBIS/Imaging/LOG_master_inclusion_list.csv")
inclusion_lists <- subset(LOG_master_inclusion_list,select=c(1,5))
inclusive <- subset(LOG_master_inclusion_list, HCPMPP_inclusive == 1 | HCPMPP_inclusive == "1f",select = c("scanID","HCPMPP_inclusive"))
# for inclusive list, include all 1Fs and make decisions later for strict list (MNI warps can be included in SA bc that's calculated in native space but CT is in MNI space)
inclusive$bidsid <- gsub("DMHDS","sub-",inclusive$scanID)
list <- na.omit(subset(inclusive,select=c(3)))
corrCT <- merge(list,corrCT_19,by="bidsid")
SA <- merge(list,SA_19,by="bidsid")
TOT <- merge(list,TOT_19,by="bidsid")
aseg <- merge(list,aseg_19,by="bidsid")
corrCT <- merge(LittleP,corrCT,by="snum")
SA <- merge(LittleP,SA,by="snum")
TOT <- merge(LittleP,TOT,by="snum")
aseg <- merge(LittleP,aseg,by="snum")
```


### basic checks and summary statistics
```{r summary}
table(is.na(TOT$SA_TOT))
table(is.na(TOT$corrCT_TOT))
hist(TOT$SA_TOT)
hist(TOT$corrCT_TOT)
mean(TOT$SA_TOT)
mean(TOT$corrCT_TOT)
sd(TOT$SA_TOT)
sd(TOT$corrCT_TOT)
```

### wholebrain analysis
```{r wholebrain}

wholebrain <- data.frame(x=c("CT","SA","BV"))
for (i in 4:9){ # columns 4-9 are B and CF factor scores
  CT_b <- summary(lm(scale(TOT$corrCT_TOT)~scale(TOT[[i]])+TOT$sex))$coefficients[2,1]
  CT_se <- summary(lm(scale(TOT$corrCT_TOT)~scale(TOT[[i]])+TOT$sex))$coefficients[2,2]
  CT_p <- summary(lm(scale(TOT$corrCT_TOT)~scale(TOT[[i]])+TOT$sex))$coefficients[2,4]
  SA_b <- summary(lm(scale(TOT$SA_TOT)~scale(TOT[[i]])+TOT$sex))$coefficients[2,1]
  SA_se <- summary(lm(scale(TOT$SA_TOT)~scale(TOT[[i]])+TOT$sex))$coefficients[2,2]
  SA_p <- summary(lm(scale(TOT$SA_TOT)~scale(TOT[[i]])+TOT$sex))$coefficients[2,4]
  BV_b <- summary(lm(scale(TOT$BV_aseg)~scale(TOT[[i]])+TOT$sex))$coefficients[2,1]
  BV_se <- summary(lm(scale(TOT$BV_aseg)~scale(TOT[[i]])+TOT$sex))$coefficients[2,2]
  BV_p <- summary(lm(scale(TOT$BV_aseg)~scale(TOT[[i]])+TOT$sex))$coefficients[2,4]
  newb <- c(CT_b,SA_b,BV_b)
  wholebrain <- cbind(wholebrain,newb)
  names(wholebrain)[ncol(wholebrain)] <- names(TOT)[i]
  newse <- c(CT_se,SA_se,BV_se)
  wholebrain <- cbind(wholebrain,newse)
  names(wholebrain)[ncol(wholebrain)] <- names(TOT)[i]
  newp <- c(CT_p,SA_p,BV_p)
  wholebrain <- cbind(wholebrain,newp)
  names(wholebrain)[ncol(wholebrain)] <- names(TOT)[i]
}
wholebrain

# confidence intervals
wholebrain[1,8]-1.96*wholebrain[1,9]; wholebrain[1,8]+1.96*wholebrain[1,9] # CT and INT
wholebrain[1,5]-1.96*wholebrain[1,6]; wholebrain[1,5]+1.96*wholebrain[1,6] # CT and EXT
wholebrain[1,11]-1.96*wholebrain[1,12]; wholebrain[1,11]+1.96*wholebrain[1,12] # CT and THD
wholebrain[1,2]-1.96*wholebrain[1,3]; wholebrain[1,2]+1.96*wholebrain[1,3] # CT and P

# checking CT for robustness with covariates, 11/3/19
wholebrain_covars <- data.frame(brainvar=character(), behavvar=character(), b=double(), lb=double(), ub=double(), n=integer(), covs=character())
for (factor in c("INT_CF","EXT_CF","THD_CF","P_B")){
    
    s <- summary(lm(scale(TOT$corrCT_TOT)~scale(TOT[factor])+TOT$sex))
    N <- sum(s$df[1:2])
    b <- s$coefficients[2,1]
    p <- s$coefficients[2,4]
    se <- s$coefficients[2,2]
    CI_lb <- b-1.96*se 
    CI_ub <- b+1.96*se 
    wholebrain_covars <- rbind(wholebrain_covars,data.frame(brainvar="CT",behavvar=factor,b=b,lb=CI_lb,ub=CI_ub,n=N,covs="sex"))
    
    s <- summary(lm(scale(TOT$corrCT_TOT)~scale(TOT[factor])+TOT$sex+scale(TOT$SESchildhd)))
    N <- sum(s$df[1:2])
    b <- s$coefficients[2,1]
    p <- s$coefficients[2,4]
    se <- s$coefficients[2,2]
    CI_lb <- b-1.96*se 
    CI_ub <- b+1.96*se 
    wholebrain_covars <- rbind(wholebrain_covars,data.frame(brainvar="CT",behavvar=factor,b=b,lb=CI_lb,ub=CI_ub,n=N,covs="sex+SESchild"))
    
    s <- summary(lm(scale(TOT$corrCT_TOT)~scale(TOT[factor])+TOT$sex+TOT$AnyRxPsych45))
    N <- sum(s$df[1:2])
    b <- s$coefficients[2,1]
    p <- s$coefficients[2,4]
    se <- s$coefficients[2,2]
    CI_lb <- b-1.96*se 
    CI_ub <- b+1.96*se 
    wholebrain_covars <- rbind(wholebrain_covars,data.frame(brainvar="CT",behavvar=factor,b=b,lb=CI_lb,ub=CI_ub,n=N,covs="sex+AnyRxPsych45"))
    
    s <- summary(lm(scale(TOT$corrCT_TOT)~scale(TOT[factor])+TOT$sex+TOT$BrainMed_bin))
    N <- sum(s$df[1:2])
    b <- s$coefficients[2,1]
    p <- s$coefficients[2,4]
    se <- s$coefficients[2,2]
    CI_lb <- b-1.96*se 
    CI_ub <- b+1.96*se 
    wholebrain_covars <- rbind(wholebrain_covars,data.frame(brainvar="CT",behavvar=factor,b=b,lb=CI_lb,ub=CI_ub,n=N,covs="sex+ScanTimeBrainMed"))
    
    s <- summary(lm(scale(TOT$corrCT_TOT)~scale(TOT[factor])+TOT$sex+scale(TOT$CHIorganVar45)))
    N <- sum(s$df[1:2])
    b <- s$coefficients[2,1]
    p <- s$coefficients[2,4]
    se <- s$coefficients[2,2]
    CI_lb <- b-1.96*se 
    CI_ub <- b+1.96*se 
    wholebrain_covars <- rbind(wholebrain_covars,data.frame(brainvar="CT",behavvar=factor,b=b,lb=CI_lb,ub=CI_ub,n=N,covs="sex+CHIorganVar45"))
    
    s <- summary(lm(scale(TOT$corrCT_TOT)~scale(TOT[factor])+TOT$sex+scale(TOT$SurfaceHoles)))
    N <- sum(s$df[1:2])
    b <- s$coefficients[2,1]
    p <- s$coefficients[2,4]
    se <- s$coefficients[2,2]
    CI_lb <- b-1.96*se 
    CI_ub <- b+1.96*se 
    wholebrain_covars <- rbind(wholebrain_covars,data.frame(brainvar="CT",behavvar=factor,b=b,lb=CI_lb,ub=CI_ub,n=N,covs="sex+SurfaceHoles"))
    
    s <- summary(lm(scale(TOT$corrCT_TOT)~scale(TOT[factor])+TOT$sex+scale(TOT$Visual.rating)))
    N <- sum(s$df[1:2])
    b <- s$coefficients[2,1]
    p <- s$coefficients[2,4]
    se <- s$coefficients[2,2]
    CI_lb <- b-1.96*se 
    CI_ub <- b+1.96*se 
    wholebrain_covars <- rbind(wholebrain_covars,data.frame(brainvar="CT",behavvar=factor,b=b,lb=CI_lb,ub=CI_ub,n=N,covs="sex+Visual.rating"))
    
    s <- summary(lm(scale(TOT$corrCT_TOT)~scale(TOT[factor])+TOT$sex+scale(TOT$AverageFD)))
    N <- sum(s$df[1:2])
    b <- s$coefficients[2,1]
    p <- s$coefficients[2,4]
    se <- s$coefficients[2,2]
    CI_lb <- b-1.96*se 
    CI_ub <- b+1.96*se 
    wholebrain_covars <- rbind(wholebrain_covars,data.frame(brainvar="CT",behavvar=factor,b=b,lb=CI_lb,ub=CI_ub,n=N,covs="sex+AverageFD"))    
}

```

###  forest plot for each variable with covariates
```{r forestplot covars}

library(RColorBrewer)

subset1 <- wholebrain_covars[wholebrain_covars$covs=="sex",]
subset2 <- wholebrain_covars[wholebrain_covars$covs=="sex+SESchild",]
subset3 <- wholebrain_covars[wholebrain_covars$covs=="sex+AnyRxPsych45",]
subset4 <- wholebrain_covars[wholebrain_covars$covs=="sex+ScanTimeBrainMed",]
subset5 <- wholebrain_covars[wholebrain_covars$covs=="sex+CHIorganVar45",]
subset6 <- wholebrain_covars[wholebrain_covars$covs=="sex+SurfaceHoles",]
subset7 <- wholebrain_covars[wholebrain_covars$covs=="sex+Visual.rating",]
subset8 <- wholebrain_covars[wholebrain_covars$covs=="sex+AverageFD",]

tabletext <- cbind(
  c("Internalizing","Externalizing","Thought","p Factor")
)

png(paste(workdir,"GlobalCT_forestWithCovars.png",sep=""),height=4,width=8,res=300,units="in")
print(forestplot(tabletext,
        hrzl_lines=list("4"=gpar(lty=1, col="grey")),
         legend=c("(sex only)","Chldhd SES","Meds (P45)", "Meds (scan)","Disease","Img Qlty: Euler","Img Qlty: manual","fMRI motion"),
        mean =cbind(subset1$b, subset2$b, subset3$b , subset4$b , subset5$b , subset6$b , subset7$b , subset8$b ),
        lower=cbind(subset1$lb,subset2$lb,subset3$lb, subset4$lb, subset5$lb, subset6$lb, subset7$lb, subset8$lb),
        upper=cbind(subset1$ub,subset2$ub,subset3$ub, subset4$ub, subset5$ub, subset6$ub, subset7$ub, subset8$ub),
        boxsize=.1,
        col=fpColors(box=c("#000000","#009E73","#0072B2","#56B4E9","mediumpurple3","#F0E442","#E69F00","#D55E00")),
           xlab="Standardized Beta" ))
dev.off()

```

### Forest plot for effect sizes for mean CT in diagnostic groups vs EMH
```{r by diagnostic group}
# values are from renate 11/5/19
# #Cohen's D
# byGroup <- data.frame(variable=c("Depression","Anxiety","Substance","Schizophrenia"),d=c(.411,.246,.419,.703),lb=c(.18,.025,.206,.272),ub=c(.643,.466,.632,1.133))
# r
byGroup <- data.frame(variable=c("Depression","Anxiety","Substance Use","Schizophrenia"),d=c(-.201,-.122,-.205,-.332),ub=c(-.09,-.013,-.103,-.135),lb=c(-.306,-.227,-.301,-.493))

tabletext <- cbind(
  # c(expr(atop("Depression",italic("N = 146"))),"Anxiety (N = 174)","Substance (N = 210)","Schizophrenia (N = 13?)")
  c(expr("Depression\n(N = 146)"),expr("Anxiety\n(N = 174)"),expr("Substance\n(N = 210)"),expr("Schizophrenia\n(N = 25)")) 
)

png(paste(workdir,"GlobalCT_forestByDiagnosticGroups_r.png",sep=""),height=4,width=8,res=300,units="in")
print( forestplot(tabletext,
        mean =byGroup$d,
        lower=byGroup$lb,
        upper=byGroup$ub,
        boxsize=.12,
        txt_gp = fpTxtGp( ticks=gpar(fontfamily="", cex=1), xlab=gpar(fontfamily="", cex=1.25) ),
         xlab="Standardized Beta" ) )
dev.off()
```


### Cortical thickness/surface area Glasser parcel-wise analysis
P_BF
```{r P structural}
#predict P_B with each Glasser parcel CT (sex as covariate)
cCT_P_B <- data.frame(bval=double(),pval=double(),se=double())
for (ROI in 17:376){
  tmpmodel=lm(scale(corrCT[[ROI]])~scale(P_B)+sex, corrCT)
  b <- summary(tmpmodel)$coefficients[2,1]
  p <- summary(tmpmodel)$coefficients[2,4]
  se <- summary(tmpmodel)$coefficients[2,2]
  cCT_P_B[nrow(cCT_P_B)+1,] <- c(b,p,se)
  row.names(cCT_P_B)[nrow(cCT_P_B)] <- names(corrCT)[[ROI]]
}
#FDR correction
cCT_P_B <- transform(cCT_P_B, adj.p = p.adjust(pval,method="BH"))
sum(cCT_P_B$adj.p<0.05)

#predict P_B with each Glasser parcel SA (sex as covariate)
SA_P_B <- data.frame(bval=double(),pval=double(),se=double())
for (ROI in 17:376){
  tmpmodel=lm(scale(SA[[ROI]])~scale(P_B)+sex, SA)
  b <- summary(tmpmodel)$coefficients[2,1]
  p <- summary(tmpmodel)$coefficients[2,4]
  se <- summary(tmpmodel)$coefficients[2,2]
  SA_P_B[nrow(SA_P_B)+1,] <- c(b,p,se)
  row.names(SA_P_B)[nrow(SA_P_B)] <- names(SA)[[ROI]]
}
#FDR correction
SA_P_B <- transform(SA_P_B, adj.p = p.adjust(pval,method="BH"))
sum(SA_P_B$adj.p<0.05)
```

EXT_CF
```{r EXT structural}
#predict EXT_CF with each Glasser parcel CT (sex as covariate)
cCT_EXT_CF <- data.frame(bval=double(),pval=double(),se=double())
for (ROI in 17:376){
  tmpmodel=lm(scale(corrCT[[ROI]])~scale(EXT_CF)+sex, corrCT)
  b <- summary(tmpmodel)$coefficients[2,1]
  p <- summary(tmpmodel)$coefficients[2,4]
  se <- summary(tmpmodel)$coefficients[2,2]
  cCT_EXT_CF[nrow(cCT_EXT_CF)+1,] <- c(b,p,se)
  row.names(cCT_EXT_CF)[nrow(cCT_EXT_CF)] <- names(corrCT)[[ROI]]
}
#FDR correction
cCT_EXT_CF <- transform(cCT_EXT_CF, adj.p = p.adjust(pval,method="BH"))
sum(cCT_EXT_CF$adj.p<0.05)

#predict EXT_CF with each Glasser parcel SA (sex as covariate)
SA_EXT_CF <- data.frame(bval=double(),pval=double(),se=double())
for (ROI in 17:376){
  tmpmodel=lm(scale(SA[[ROI]])~scale(EXT_CF)+sex, SA)
  b <- summary(tmpmodel)$coefficients[2,1]
  p <- summary(tmpmodel)$coefficients[2,4]
  se <- summary(tmpmodel)$coefficients[2,2]
  SA_EXT_CF[nrow(SA_EXT_CF)+1,] <- c(b,p,se)
  row.names(SA_EXT_CF)[nrow(SA_EXT_CF)] <- names(SA)[[ROI]]
}
#FDR correction
SA_EXT_CF <- transform(SA_EXT_CF, adj.p = p.adjust(pval,method="BH"))
sum(SA_EXT_CF$adj.p<0.05)
```

INT_CF
```{r INT structural}
#predict INT_CF with each Glasser parcel CT (sex as covariate)
cCT_INT_CF <- data.frame(bval=double(),pval=double(),se=double())
for (ROI in 17:376){
  tmpmodel=lm(scale(corrCT[[ROI]])~scale(INT_CF)+sex, corrCT)
  b <- summary(tmpmodel)$coefficients[2,1]
  p <- summary(tmpmodel)$coefficients[2,4]
  se <- summary(tmpmodel)$coefficients[2,2]
  cCT_INT_CF[nrow(cCT_INT_CF)+1,] <- c(b,p,se)
  row.names(cCT_INT_CF)[nrow(cCT_INT_CF)] <- names(corrCT)[[ROI]]
}
#FDR correction
cCT_INT_CF <- transform(cCT_INT_CF, adj.p = p.adjust(pval,method="BH"))
sum(cCT_INT_CF$adj.p<0.05)

#predict INT_CF with each Glasser parcel SA (sex as covariate)
SA_INT_CF <- data.frame(bval=double(),pval=double(),se=double())
for (ROI in 17:376){
  tmpmodel=lm(scale(SA[[ROI]])~scale(INT_CF)+sex, SA)
  b <- summary(tmpmodel)$coefficients[2,1]
  p <- summary(tmpmodel)$coefficients[2,4]
  se <- summary(tmpmodel)$coefficients[2,2]
  SA_INT_CF[nrow(SA_INT_CF)+1,] <- c(b,p,se)
  row.names(SA_INT_CF)[nrow(SA_INT_CF)] <- names(SA)[[ROI]]
}
#FDR correction
SA_INT_CF <- transform(SA_INT_CF, adj.p = p.adjust(pval,method="BH"))
sum(SA_INT_CF$adj.p<0.05)
```

THD_CF
```{r THD structural}
#predict THD_CF with each Glasser parcel CT (sex as covariate)
cCT_THD_CF <- data.frame(bval=double(),pval=double(),se=double())
for (ROI in 17:376){
  tmpmodel=lm(scale(corrCT[[ROI]])~scale(THD_CF)+sex, corrCT)
  b <- summary(tmpmodel)$coefficients[2,1]
  p <- summary(tmpmodel)$coefficients[2,4]
  se <- summary(tmpmodel)$coefficients[2,2]
  cCT_THD_CF[nrow(cCT_THD_CF)+1,] <- c(b,p,se)
  row.names(cCT_THD_CF)[nrow(cCT_THD_CF)] <- names(corrCT)[[ROI]]
}
#FDR correction
cCT_THD_CF <- transform(cCT_THD_CF, adj.p = p.adjust(pval,method="BH"))
sum(cCT_THD_CF$adj.p<0.05)

#predict THD_CF with each Glasser parcel SA (sex as covariate)
SA_THD_CF <- data.frame(bval=double(),pval=double(),se=double())
for (ROI in 17:376){
  tmpmodel=lm(scale(SA[[ROI]])~scale(THD_CF)+sex, SA)
  b <- summary(tmpmodel)$coefficients[2,1]
  p <- summary(tmpmodel)$coefficients[2,4]
  se <- summary(tmpmodel)$coefficients[2,2]
  SA_THD_CF[nrow(SA_THD_CF)+1,] <- c(b,p,se)
  row.names(SA_THD_CF)[nrow(SA_THD_CF)] <- names(SA)[[ROI]]
}
#FDR correction
SA_THD_CF <- transform(SA_THD_CF, adj.p = p.adjust(pval,method="BH"))
sum(SA_THD_CF$adj.p<0.05)
```

### CT: Explore overlapping parcels
```{r overlaps}
# ARK
sum(cCT_INT_CF$adj.p<.05 & cCT_EXT_CF$adj.p>.05 & cCT_THD_CF$adj.p>.05 & cCT_P_B$adj.p>.05)
sum(cCT_EXT_CF$adj.p<.05 & cCT_INT_CF$adj.p>.05 & cCT_THD_CF$adj.p>.05 & cCT_P_B$adj.p>.05)
sum(cCT_THD_CF$adj.p<.05 & cCT_INT_CF$adj.p>.05 & cCT_EXT_CF$adj.p>.05 & cCT_P_B$adj.p>.05)
sum(cCT_P_B$adj.p<.05 & cCT_INT_CF$adj.p>.05 & cCT_EXT_CF$adj.p>.05 & cCT_THD_CF$adj.p>.05)

sum(cCT_INT_CF$adj.p<.05 & cCT_P_B$adj.p>.05)
sum(cCT_EXT_CF$adj.p<.05 & cCT_P_B$adj.p>.05)
sum(cCT_THD_CF$adj.p<.05 & cCT_P_B$adj.p>.05)

sum(cCT_INT_CF$adj.p<.05 & cCT_P_B$adj.p<.05)/sum(cCT_P_B$adj.p<.05)
sum(cCT_EXT_CF$adj.p<.05 & cCT_P_B$adj.p<.05)/sum(cCT_P_B$adj.p<.05)
sum(cCT_THD_CF$adj.p<.05 & cCT_P_B$adj.p<.05)/sum(cCT_P_B$adj.p<.05)

```

### CT: Explore parcels associated with each of the 3 CFs factor while controling for the others
```{r CT unique parcels}
#predict P_B with each Glasser parcel CT (sex as covariate)
cCT_3CFs_INT <- data.frame(bval=double(),pval=double(),se=double())
cCT_3CFs_EXT <- data.frame(bval=double(),pval=double(),se=double())
cCT_3CFs_THD <- data.frame(bval=double(),pval=double(),se=double())
cCT_BI_INT <- data.frame(bval=double(),pval=double(),se=double())
cCT_BI_EXT <- data.frame(bval=double(),pval=double(),se=double())

for (ROI in 21:380){

  tmpmodel <- lm(scale(corrCT[[ROI]])~scale(INT_CF)+scale(EXT_CF)+scale(THD_CF)+sex, corrCT)

  b <-  summary(tmpmodel)$coefficients[2,1]
  p <-  summary(tmpmodel)$coefficients[2,4]
  se <- summary(tmpmodel)$coefficients[2,2]
  cCT_3CFs_INT[nrow(cCT_3CFs_INT)+1,] <- c(b,p,se)
  row.names(cCT_3CFs_INT)[nrow(cCT_3CFs_INT)] <- names(corrCT)[[ROI]]

  b <-  summary(tmpmodel)$coefficients[3,1]
  p <-  summary(tmpmodel)$coefficients[3,4]
  se <- summary(tmpmodel)$coefficients[3,2]
  cCT_3CFs_EXT[nrow(cCT_3CFs_EXT)+1,] <- c(b,p,se)
  row.names(cCT_3CFs_EXT)[nrow(cCT_3CFs_EXT)] <- names(corrCT)[[ROI]]

  b <-  summary(tmpmodel)$coefficients[4,1]
  p <-  summary(tmpmodel)$coefficients[4,4]
  se <- summary(tmpmodel)$coefficients[4,2]
  cCT_3CFs_THD[nrow(cCT_3CFs_THD)+1,] <- c(b,p,se)
  row.names(cCT_3CFs_THD)[nrow(cCT_3CFs_THD)] <- names(corrCT)[[ROI]]
  
  tmpmodel <- lm(scale(corrCT[[ROI]])~scale(INT_B)+scale(EXT_B)+sex, corrCT)
  
  b <-  summary(tmpmodel)$coefficients[2,1]
  p <-  summary(tmpmodel)$coefficients[2,4]
  se <- summary(tmpmodel)$coefficients[2,2]
  cCT_BI_INT[nrow(cCT_BI_INT)+1,] <- c(b,p,se)
  row.names(cCT_BI_INT)[nrow(cCT_BI_INT)] <- names(corrCT)[[ROI]]

  b <-  summary(tmpmodel)$coefficients[3,1]
  p <-  summary(tmpmodel)$coefficients[3,4]
  se <- summary(tmpmodel)$coefficients[3,2]
  cCT_BI_EXT[nrow(cCT_BI_EXT)+1,] <- c(b,p,se)
  row.names(cCT_BI_EXT)[nrow(cCT_BI_EXT)] <- names(corrCT)[[ROI]]
  
}

#FDR correction
cCT_3CFs_INT <- transform(cCT_3CFs_INT, adj.p = p.adjust(pval,method="BH"))
sum(cCT_3CFs_INT$adj.p<0.05)
cCT_3CFs_EXT <- transform(cCT_3CFs_EXT, adj.p = p.adjust(pval,method="BH"))
sum(cCT_3CFs_EXT$adj.p<0.05)
cCT_3CFs_THD <- transform(cCT_3CFs_THD, adj.p = p.adjust(pval,method="BH"))
sum(cCT_3CFs_THD$adj.p<0.05)

cCT_BI_INT <- transform(cCT_BI_INT, adj.p = p.adjust(pval,method="BH"))
sum(cCT_BI_INT$adj.p<0.05)
cCT_BI_EXT <- transform(cCT_BI_EXT, adj.p = p.adjust(pval,method="BH"))
sum(cCT_BI_EXT$adj.p<0.05)

#write out for EXT, only factor with regions passing FDR threshold
write.csv(cCT_3CFs_EXT[c("bval","adj.p")], file=paste(workdir,"Glasser_EXT_ctrl.INT.THD.sex.csv",sep=""), row.names=TRUE)
write.csv(cCT_BI_EXT[c("bval","adj.p")], file=paste(workdir,"Glasser_EXTBI_ctrl.INT.sex.csv",sep=""), row.names=TRUE)

```

## Plots

## forest plots for subcortical regions
```{r aseg plots}

df_list <- list(aseg_P_B,aseg_INT_CF,aseg_EXT_CF,aseg_THD_CF)
names <- c("aseg_P_B","aseg_INT_CF","aseg_EXT_CF","aseg_THD_CF")

for ( i in 1:length(df_list) ) {
  
  df <- df_list[[i]]
  
  bilat <- df[!grepl("Left", rownames(df)) & !grepl("Right", rownames(df)) & !grepl("Bilat", rownames(df)), ]
  subset1 <- rbind(df[grepl("Bilat",rownames(df)),],bilat)
  subset2 <- rbind(df[grepl("Left",rownames(df)),],bilat)
  subset3 <- rbind(df[grepl("Right",rownames(df)),],bilat)
  
  tabletext <- cbind(
    sub("Left.","",rownames(subset2))
  )
  
  # highlight values surviving correction
  fpType_list <- list()
  for ( j in 1:nrow(subset1) ){
    if(subset2[j,"adj.p"]<.05){ t2 <- fpDrawDiamondCI } else { t2 <- fpDrawNormalCI }
    if(subset3[j,"adj.p"]<.05){ t3 <- fpDrawDiamondCI } else { t3 <- fpDrawNormalCI }
    fpType_list[[j]]=list(t2,t3)
  }
  # v1, grouped by R/L
  png(paste(workdir,"forest_subcort_",names[i],"_RL.png",sep=""),height=6,width=8,res=300,units="in")
  print(forestplot(tabletext,
             legend=c("Left", "Right"),
            fn.ci_norm=fpType_list,
          mean  = cbind(subset2$bval, subset3$bval),
          lower = cbind(subset2$bval - 1.96*subset2$se, subset3$bval - 1.96*subset3$se),
          upper = cbind(subset2$bval + 1.96*subset2$se, subset3$bval + 1.96*subset3$se),
          col=fpColors(box=c("black","lightblue")),
          boxsize=.15,
             xlab="Standardized Beta" ))
  dev.off()
  
  ### just bilateral
  # highlight values surviving correction
  fpType_list <- list()
  for ( j in 1:nrow(subset1) ){
    if(subset1[j,"adj.p"]<.05){ t1=fpDrawDiamondCI } else { t1=fpDrawNormalCI }
    fpType_list[[j]]=list(t1)
  }
  png(paste(workdir,"forest_subcort_",names[i],"_bilat.png",sep=""),height=6,width=8,res=300,units="in")
  print(forestplot(tabletext,
          mean  = cbind(subset1$bval),
          lower = cbind(subset1$bval - 1.96*subset1$se),
          upper = cbind(subset1$bval + 1.96*subset1$se),
          boxsize=.15,
             xlab="Standardized Beta" ))
  dev.off()
  
  
}
```

### correlations between factor parcelwise CT effects (fig. 3a)
```{r CT CF cor plot}
corrCF <- subset(cCT_P_B, select=c("bval"))
corrCF <- cbind(corrCF, cCT_INT_CF$bval, cCT_EXT_CF$bval, cCT_THD_CF$bval)
names(corrCF) <- c('P','INT','EXT','THD')
ggcorr(corrCF, method=c("everything","pearson"), label="TRUE", label_round=4)
```

### correlations between factors (fig. 3b)
```{r CF cor plot}
corrP <- subset(TOT,select=c("P_B"))
corrP <- cbind(corrP, TOT$INT_CF, TOT$EXT_CF, TOT$THD_CF)
names(corrP) <- c('P','INT','EXT','THD')
ggcorr(corrP, method=c("everything","pearson"), label="TRUE", label_round=4)
```




